\sysfull

### 2018-08-07 paper/asplos19/paging.tex
minor changes

Resolving WAR (Write-After-Read) dependencies by considering static task boundaries is not sufficient to keep non-volatile memory consistent when task are coalesced. Not handing WAR dependencies with task coalescing introduces a new problem, which we denote as \emph{task coalescing-induced WAR dependency}. This problem is illustrated in Fig.~\ref{figure:coalescedWar}. Therefore, \sys implements novel {\em Virtual Memory Manager} (WMM) which enables task coalescing guaranteeing data integrity, which is at the same time efficient.

@@

After address translation (Fig.~\ref{figure:mem-man}, Step 6), a task accesses the protected variable's location in the volatile \texttt{working} buffer (Step 7). The PP keeps track of the page tags for the pages currently resident in the \texttt{working} buffer. When a task accesses a variable, it compares the variable's page tag to tags of the pages in {\tt working} (Algorithm~\ref{algo:rwar}, Line 2). If the accessed variable's page tag is not found in the page buffer, the operation incurs a {\em page fault} (Line 4). The byte is accessed in the page buffer at the index of the resident page and the variable's page offset (Lines 5--6).

@@

\paragraph{Memory Consistency.}
\sys's paging mechanism ensures that a task only ever executes using consistent protected data. During task execution, modifications to protected data do not affect the \texttt{\underline{private}} buffer, because a task reads and writes the volatile \texttt{working} buffer only, and modified pages are kept in \texttt{\underline{shadow}} until commit. A power failure erases the contents of the \texttt{working} buffer, preventing a re-executing task from observing updates from a previous execution attempt. Clearing \texttt{\underline{shadowCount}} as part of the second phase commit (Line 14) ensures that all accesses to protected variables in subsequent tasks correctly access their consistent memory locations in \texttt{\underline{private}}. This solves coalescing-induced WAR dependency problem (see Fig.~\ref{figure:coalescedWar} again).

@@

\sys asks the programmer to use its {\tt RP} and {\tt WP} API methods on every access to a protected variable (cf. Section~\ref{sec:coala_api}). These API invocations present a risk of high overhead because there is a dynamic check on every read and write. Despite the risk of per-access overhead, \sys's dynamic memory protection scheme brings several benefits over a static approach (i.e.,~\cite{alpaca}). First, the limitations of static analysis preclude some uses of pointers due to potential pointer aliasing. For example, in the presence of arbitrary pointer operations, a function call using a function pointer, or an interrupt within a task, the system cannot statically analyze the memory behavior. Second, a static approach \textit{cannot handle task coalescing}, because a protected variable's lifetime, i.e., from first use to commit, is unknown at compile time. \sys's dynamic, per-access instrumentation supports arbitrary use of pointers and enables task coalescing.

>>>>

Resolving WAR (Write-After-Read) dependencies by considering static task boundaries is not sufficient to keep non-volatile memory consistent when tasks are coalesced. Not handling WAR dependencies with task coalescing introduces a new problem, which we denote as \emph{task coalescing-induced WAR dependency}. This problem is illustrated in Fig.~\ref{figure:coalescedWar}. Therefore, \sys implements novel {\em Virtual Memory Manager} (VMM) which enables task coalescing guaranteeing data integrity, which is at the same time efficient.

@@

After address translation (Fig.~\ref{figure:mem-man}, Step 6), a task accesses the protected variable's location in the volatile \texttt{working} buffer (Step 7). The VMM keeps track of the page tags for the pages currently resident in the \texttt{working} buffer. When a task accesses a variable, it compares the variable's page tag to tags of the pages in {\tt working} (Algorithm~\ref{algo:rwar}, Line 2). If the accessed variable's page tag is not found in the page buffer, the operation incurs a {\em page fault} (Line 4). The byte is accessed in the page buffer at the index of the resident page and the variable's page offset (Lines 5--6).

@@

\paragraph{Memory Consistency.}
\sys's paging mechanism ensures that a task only ever executes using consistent protected data. During task execution, modifications to protected data do not affect the \texttt{\underline{private}} buffer, because a task reads and writes the volatile \texttt{working} buffer only, and modified pages are kept in \texttt{\underline{shadow}} until commit. A power failure erases the contents of the \texttt{working} buffer, preventing a re-executing task from observing updates from a previous execution attempt. Clearing \texttt{\underline{shadowCount}} as part of the second phase commit (Line 14) ensures that all accesses to protected variables in subsequent tasks correctly access their consistent memory locations in \texttt{\underline{private}}. This solves the coalescing-induced WAR dependency problem (see Fig.~\ref{figure:coalescedWar} again).

@@

\sys asks the programmer to use its {\tt RP} and {\tt WP} API methods on every access to a protected variable (cf. Section~\ref{sec:coala_api}). These API invocations present a risk of high overhead because there is a dynamic check on every read and write. Despite the risk of per-access overhead, \sys's dynamic memory protection scheme brings several benefits over a static approach (i.e.,~\cite{alpaca}). First, the limitations of static analysis preclude some uses of pointers due to potential pointer aliasing. For example, in the presence of arbitrary pointer operations, a function call using a function pointer, or an interrupt within a task, the system cannot statically analyze the memory behavior. Second, a static approach \textit{cannot handle task coalescing}, because a protected variable's lifetime, i.e., from first use to commit, is unknown at compile-time. \sys's dynamic, per-access instrumentation supports arbitrary use of pointers and enables task coalescing.
